The Globular Cluster System of the Auriga Simulations

### 2019-03-25 AurigaGCS.tex
Added plot of mean vs stdev of FeH and Rgc distributions

\section{Introduction}
Globular clusters (GC)s are omnipresent, bright, old, and amongst the simplest
stellar configurations in the Universe. Their visbility and ubiquity make it 
possible to obtain integrated GC quantities of galaxies in the Local Group. 
Moreover, GCs inherit characteristics from their natal gas and GC systems show 
correlations with properties of (the field stars in) their host galaxies. For 
example, the mean metallicity of GC systems in early-type galaxies correlates with 
the galactic metallicity (van den Bergh 1975, Brodie \& Huchra 1991) as well as 
with the luminosity and possibly the mass (Larsen 2001; Peng 2006). The old ages
are consistent with formation before, during, or shortly after the initial
collapse of the proto-galaxy. In theory, all of these characteristics make GC
systems excellent tracers of the formation and evolution of their parent galaxies,
if the formation of GCs themselves is well-understood.

Most galaxies host GC systems with a bimodal colour distribution, indicative of
a bimodal metallicity distribution. The Milky Way (MW) GC system (GCS) can be
split up in a metal-rich (red) and metal-poor (blue) subpopulation divided at
[Fe/H]~$=-1$ \citep[e.g.][]{Harris2001}, although slightly different values can
also be found in the literature. The two subpopulations are believed to be
associated to the galactic disk, respectively the stellar halo 
\citep{1985ApJ...293..424Z}. The latter is supported by observed similarities 
between the spatial distribution and chemical signature of the `blue' GCs show 
and stars in the stellar halo \citep{2008A&ARv..15..145H}. Moreover, relative 
age-estimates show an offset of $1.5$~Gyr between both subpopulations 
\citep{2005AJ....130..116D}.

\citet{2006ARA&A..44..193B} review extragalactic GCs and galaxy 
formation, and argue that the observed metal-rich and metal-poor

@@

\subsubsection*{Distribution of total GC mass in metallicity-radial bins}
In Fig.~\ref{fig:MW-FeHRgc} we show the two-dimensional mass-weighted 
metallicity-radial distribution of the MW GCS. In Sec.~\ref{sec:FeHRgc} 
we investigate whether the star formation model implemented in the Auriga 
simulations can produce sufficient total mass in GC candidates in the same bins.

@@

We present a mass-weighted histogram of the age-estimates of the $55$ MW GCs in V13
and $85$ GCs in M31 for which age-estimates are available in CR16, see 
Fig.~\ref{fig:MW-M31-age}.

\begin{figure}
    \includegraphics[width=\columnwidth]{{MW_M31_Age_HistogramMassWeighted}.png}
    \caption{
        Mass-weighted age distribution of 55 GCs in the MW
        \citep[data from][]{2013ApJ...775..134V} and 85 GCs
        in M31 \citep[data from][]{2016ApJ...824...42C}.
        \label{fig:MW-M31-age}
    }
\end{figure}

@@

\section{Results}
\label{sec:results}
We define GC candidates in the Auriga simulations as all star particles older 
than $10$~Gyr based on the age distribution of the MW GCS in 
Fig.~\ref{fig:MW-M31-age} and following \citet{2017MNRAS.465.3622R}.

Through out the analysis we use six sub sets of star particles: 
\emph{all stars}, and \emph{old stars} (age $>10$~Gyr, GC candidates hereafter). 
Both sub sets are further split up in (old) star particles that have formed 
\emph{in-situ} (bound to the most-massive halo/subhalo in the first snapshot that 
the star particle was recorded), and (old) \emph{accreted} star particles (i.e. 
those that have formed ex-situ and are bound to the most-massive halo/subhalo
at $z=0$).

In Sec.~\ref{sec:metallicity} we investigate the metallicity distribution of the
GC candidates, in Sec.~\ref{sec:radial} we show the distribution of galactocentric
radii of the globular cluster candidates within the Auriga simulations, and we 
combine both in Sec.~\ref{sec:FeHRgc}. 
% We continue our analysis with an investigation
% of the properties of the proto-galaxies at times of birth of the accreted globular 
% cluster population in Sec.~\ref{sec:birth-properties-of-accreted-gc-candidates}

\subsection{Metallicity distribution}
\label{sec:metallicity}
We investigate whether the star formation model implemented in the Auriga 
simulations is capable of producing sufficient mass in old star particles in 
each metallicity bin in comparison to the Milky Way and Andromeda globular 
cluster systems. In Fig.~\ref{fig:FeH} we show a mass-weighted metallicity 
distribution where the lines show the median value of all thirty Auriga level 4 
haloes for \emph{all stars} (orange dotted), \emph{old stars / GC candidates} 
(orange solid), \emph{old in-situ} stars (blue solid), and \emph{old accreted} stars
(red solid). The shaded regions indicate the $1\sigma$ interval around the median 
(i.e. the scatter between runs with different initial conditions and merger
histories). The MW (M31) GCS is shown in purple (magenta). We use the 
same bin sizes for the simulations as for the observations, explicitly shown for
the observed profiles.

@@

@@

Therefore we investigate the over-production of simulated mass in the metallicity
and radial bins and use the term `efficiency' to refer to the combined product
of bound cluster formation and globular cluster disruption. In Fig.~\ref{fig:todo} 
we show the efficiencies that we find when we compare the simulations to the 
globular cluster systems of the Milky Way as well as that of Andromeda (M31).

@@

\subsection{Age cut}
Although the age distribution of M31 Perhaps an age cut of 6~Gyr would would be more 
appropriate for M31, see Fig.~\ref{fig:MW-M31-age}.

@@

Fig.~\ref{fig:logMFeH_res} shows the mass-weighted metallicity distribution, 
Fig.~\ref{fig:logMRgc_res} shows the mass-weighted radial distribution, and
Fig.~\ref{fig:logMRgcFeH_res}

\begin{figure*}
    \includegraphics[width=0.31\textwidth]{{logMFeH_Au6}.png}
    \includegraphics[width=0.31\textwidth]{{logMFeH_Au16}.png}
    \includegraphics[width=0.31\textwidth]{{logMFeH_Au24}.png}
    \caption{Same as Fig.~\ref{fig:FeH}, but here the colours indicate resolution
        level: L3 green, L4 orange, and L5 blue. \emph{Left:} Auriga halo 6.
        \emph{Mid:} Auriga halo 16. \emph{Right:} Auriga halo 24. For all three
        haloes we find marginal increases in the mass normalization with increasing 
        resolution level.
        \label{fig:logMFeH_res}
    }

\end{figure*}
\begin{figure*}
    \includegraphics[width=0.31\textwidth]{{logMRgc_Au6}.png}
    \includegraphics[width=0.31\textwidth]{{logMRgc_Au16}.png}
    \includegraphics[width=0.31\textwidth]{{logMRgc_Au24}.png}
    \caption{Same as Fig.~\ref{fig:Rgc}, but here the colours indicate resolution
        level: L3 green, L4 orange, and L5 blue. \emph{Left:} Auriga halo 6.
        \emph{Mid:} Auriga halo 16. \emph{Right:} Auriga halo 24. For all three 
        haloes we find marginal increases in the mass normalization with increasing 
        resolution level.
        \label{fig:logMRgc_res}
    }

>>>>

\section{Introduction}
Globular clusters (GC)s are omnipresent, bright, old, and amongst the simplest
stellar configurations in the Universe. Their visbility and ubiquity make it 
possible to obtain integrated GC quantities within the Virgo Supercluster.
Moreover, GCs inherit characteristics from their natal gas and GC systems show 
correlations with properties of (the field stars in) their host galaxies.
% For 
% example, the mean metallicity of GC systems in early-type galaxies correlates with 
% the galactic metallicity (van den Bergh 1975, Brodie \& Huchra 1991) as well as 
% with the luminosity, and possibly the mass (Larsen 2001; Peng 2006).
The old ages
are consistent with formation before, during, or shortly after the initial
collapse of the proto-galaxy and GCs have been present within galaxies for nearly
a Hubble time. In theory, all of these characteristics make GC systems excellent
tracers of the formation and evolution of their parent galaxies, if the formation 
of GCs themselves is well-understood.

Most galaxies host GC systems with a bimodal colour distribution, indicative of
a bimodal metallicity distribution. The Milky Way (MW) GC system (GCS) can be
split up in a metal-rich (red) and metal-poor (blue) subpopulation divided at
[Fe/H]~$=-1$ \citep[e.g.][]{Harris2001}, although slightly different values can
also be found in the literature. The two subpopulations are believed to be
associated to the galactic disk, respectively the stellar halo 
\citep[e.g.][]{1985ApJ...293..424Z}. The latter is supported by observed similarities 
between the spatial distribution and chemical signature of the `blue' GCs show 
and stars in the stellar halo \citep{2008A&ARv..15..145H}. Moreover, relative 
age-estimates indicate that the metal-poor subpopulation may be $1.5$~Gyr younger 
than the metal-rich counterpart \citep{2005AJ....130..116D}.

Several formation scenarios could explain the observed bimodality, see 
\citet{2006ARA&A..44..193B} for a review of extragalactic GCs and galaxy 
formation. The authors argue that the observed metal-rich and metal-poor

@@

\subsubsection*{Distribution of total GC mass in metallicity-radial bins}
In Figure~\ref{fig:MW-FeHRgc} we show the two-dimensional mass-weighted 
metallicity-radial distribution of the MW GCS. In Sec.~\ref{sec:FeHRgc} 
we investigate whether the star formation model implemented in the Auriga 
simulations can produce sufficient total mass in GC candidates in the same bins.

@@

We present a mass-weighted histogram of the age-estimates of the $55$ MW GCs in V13
and $85$ GCs in M31 for which age-estimates are available in CR16, see 
Figure~\ref{fig:MW-M31-age}.

\begin{figure}
    \includegraphics[width=\columnwidth]{{MW_M31_Age_HistogramMassWeighted_Msun}.png}
    \caption{
        Mass-weighted age distribution of 55 GCs in the MW
        \citep[data from][]{2013ApJ...775..134V} and 85 GCs
        in M31 \citep[data from][]{2016ApJ...824...42C}.
        \label{fig:MW-M31-age}
    }
\end{figure}

@@

\section{Results}
\label{sec:results}
We define GC candidates in the Auriga simulations as all star particles older 
than $10$~Gyr based on the MW GCS age distribution (Figure~\ref{fig:MW-M31-age}),
and following \citet{2017MNRAS.465.3622R}.

Trough out the analysis we mainly use three subsets of star particles, the 
\emph{old stars} (age $>10$~Gyr, or GC candidates), the \emph{old insitu} stars
(defined as those bound to the most-massive halo/subhalo in the first snapshot 
that the particle was recorded), and the \emph{old accreted} star particles
(i.e. those that have formed ex-situ and are bound to the most-massive halo/subhalo 
at $z=0$). In addition, we include \emph{all stars} (no selection criterion) to 
examine the result of (not) applying an age cut to our selection functions.

We consider the metallicity distribution in Sec.~\ref{sec:metallicity} 
the distribution of galactocentric radii in Sec.~\ref{sec:radial}, and the
combination of both in Sec.~\ref{sec:FeHRgc}.

\subsection{Metallicity distribution}
\label{sec:metallicity}
We investigate whether the star formation model implemented in the Auriga 
simulations is capable of i) producing a metallicity distribution that is 
consistent with the GCS observed in the MW (M31), and ii) generating sufficient 
mass over the full domain of the observations.

In Figure~\ref{fig:FeH} we show a mass-weighted metallicity 
distribution where the lines show the median value of all thirty Auriga level 4 
haloes for \emph{all stars} (orange dotted), \emph{old stars / GC candidates} 
(orange solid), \emph{old in-situ} stars (blue solid), and \emph{old accreted} stars
(red solid). The shaded regions indicate the $1\sigma$ interval around the median 
(i.e. the scatter between runs with different initial conditions and merger
histories). The MW (M31) GCS is shown in purple (magenta). We use the 
same bin sizes for the simulations as for the observations, explicitly shown for
the observed profiles.

\begin{figure}
    \includegraphics[width=\columnwidth]{{FeH_mu_sigma}.png}
    \caption{
        \label{fig:FeH_mu_sigma}
    }
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{Rgc_mu_sigma}.png}
    \caption{
        \label{fig:Rgc_mu_sigma}
    }
\end{figure}

@@

Therefore we investigate the over-production of simulated mass in the metallicity
and radial bins and use the term `efficiency' to refer to the combined product
of bound cluster formation and globular cluster disruption. In Figure~\ref{fig:todo} 
we show the efficiencies that we find when we compare the simulations to the 
globular cluster systems of the Milky Way as well as that of Andromeda (M31).

@@

\subsection{Age cut}
Although the age distribution of M31 Perhaps an age cut of 6~Gyr would would be more 
appropriate for M31, see Figure~\ref{fig:MW-M31-age}.

@@

Figure~\ref{fig:logMFeH_res} shows the mass-weighted metallicity distribution, 
Figure~\ref{fig:logMRgc_res} shows the mass-weighted radial distribution, and
Figure~\ref{fig:logMRgcFeH_res}

\begin{figure*}
    \includegraphics[width=0.31\textwidth]{{logMFeH_Au6}.png}
    \includegraphics[width=0.31\textwidth]{{logMFeH_Au16}.png}
    \includegraphics[width=0.31\textwidth]{{logMFeH_Au24}.png}
    \caption{Same as Figure~\ref{fig:FeH}, but here the colours indicate resolution
        level: L3 green, L4 orange, and L5 blue. \emph{Left:} Auriga halo 6.
        \emph{Mid:} Auriga halo 16. \emph{Right:} Auriga halo 24. For all three
        haloes we find marginal increases in the mass normalization with increasing 
        resolution level.
        \label{fig:logMFeH_res}
    }

\end{figure*}
\begin{figure*}
    \includegraphics[width=0.31\textwidth]{{logMRgc_Au6}.png}
    \includegraphics[width=0.31\textwidth]{{logMRgc_Au16}.png}
    \includegraphics[width=0.31\textwidth]{{logMRgc_Au24}.png}
    \caption{Same as Figure~\ref{fig:Rgc}, but here the colours indicate resolution
        level: L3 green, L4 orange, and L5 blue. \emph{Left:} Auriga halo 6.
        \emph{Mid:} Auriga halo 16. \emph{Right:} Auriga halo 24. For all three 
        haloes we find marginal increases in the mass normalization with increasing 
        resolution level.
        \label{fig:logMRgc_res}
    }
